\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape TAI Cho Fung Woody} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 852-5929 7902 ~ 
    \href{mailto:woodytai.secondary.hk@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{woodytai.secondary.hk@gmail.com}} ~ 
    \href{https://linkedin.com/in/woody-tai/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/woody-tai}}  
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeItemListStart
    \resumeSubheading
      {The Chinese Foundation Secondary School}{2021-2027}
      {High School Diploma}{Hong Kong}
    \resumeSubheading
      {Hong Kong Academy for Gifted Education (HKAGE)}{2023-Present}
      {Student Member}{Hong Kong}
  \resumeItemListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeItemListStart
    \resumeSubheading
      {CUHK Faculty of Science}{May 2024 -- September 2024}
      {Research Intern}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Assisted in research projects focused on biochemistry and molecular biology, contributing to data analysis and experiments.}
        \resumeItem{Presented findings and progress updates to faculty and peers, enhancing communication skills.}
      \resumeItemListEnd

    \resumeSubheading
      {Model United Nations}{April 2024 -- Present}
      {Founder and Head Delegate}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Led delegation to achieve recognition for outstanding performance in debates and discussions.}
        \resumeItem{Organized training sessions to improve public speaking and negotiation skills.}
      \resumeItemListEnd

    \resumeSubheading
      {Harvard Project for Asian and International Relations}{August 2023}
      {Special Delegate}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Developed web applications using Python and integrated SQL databases to enhance user experience.}
        \resumeItem{Collaborated with a diverse group of delegates to discuss sustainable solutions.}
      \resumeItemListEnd
  \resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeItemListStart
    \resumeSubheading
      {Preface NOMAD Awards}{August 2023}
      {Delegate}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Developed web applications using Python and integrated SQL databases to enhance user experience.}
      \resumeItemListEnd
  \resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} Python, Java, C, HTML/CSS, JavaScript, SQL}
    \resumeItem{\textbf{Developer Tools:} VS Code, Google Cloud Platform}
    \resumeItem{\textbf{Technologies/Frameworks:} Linux, Git, Jenkins}
  \resumeItemListEnd

%-----------HONORS AND AWARDS-----------
\section{Honors and Awards}
  \resumeItemListStart
    \resumeItem{Soyvestor STEAM Education Module B - Sustainable Agricultural \& Environment, 2022}
    \resumeItem{IELTS - Overall Score: 8, July 2023}
    \resumeItem{Best Delegate at MUNESCO(HK), 2024}
    \resumeItem{Outstanding Delegate at MUNESCO(INT), 2024}
    \resumeItem{Best Delegate at IEMUN, 2024}
    \resumeItem{Best Delegate at HVSMUN, 2024}
    \resumeItem{Best Delegate at ISSIAMUN, 2024}
    \resumeItem{Honorable Mention at LPCMUN, 2025}
  \resumeItemListEnd

%-----------LEADERSHIP / EXTRACURRICULAR-----------
\section{Leadership / Extracurricular}
  \resumeItemListStart
    \resumeSubheading
      {Model United Nations}{April 2024 -- Present}
      {Founder and Head Delegate}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Led delegation to achieve recognition for outstanding performance in debates and discussions.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Council}{May 2023 -- October 2023}
      {General Officer}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Managed social media accounts, doubling the follower count and maintaining over 90\% attendance for meetings.}
        \resumeItem{Engaged incoming students during outreach events and provided input for partnerships under the QE fund.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Club}{September 2023 -- Present}
      {Chairperson}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Organized technology conferences and taught events, providing insights for future collaborations.}
        \resumeItem{Oversaw planning and execution of club activities, ensuring student engagement.}
      \resumeItemListEnd
  \resumeItemListEnd

\end{document}
